---
title: "nlmixr2_ER"
format: html
---

# Introduction

Welcome to the learning series, where I explore introductory concepts in pharmacometrics through examples. This post comprises my experience learning about exposure-response (E-R) modeling. The FDA has 
published a wonderful guidance on E-R modeling, and how sponsors can best analyze clinical trial data to 
make informed recommendations for an investigational agent's safety-efficacy profile. 

```{r} 
# manual call of all necessary packages 
library(tidyverse)
library(nlmixr2)
```

# Dataset Preparation

```{r}
# reading source dataset into R dataframe
df <- read.csv()

# using dplyr to clean/tidy data from source

df <- df %>%
  mutate() %>%
  filter() %>%
```

# Exploratory Data Analysis

```{r}

ggplot(df, aes(x = , y = , color = factor())) + 
  geom_line() + 
  geom_smooth()

```

# Model Building

```{r}

drugX <- function() {
  ini({
    tcl <- log()
    tv <- log()
    ##var
    eta.cl + eta.v ~ c(1, 
                       0.01, 1) ##equiv. to $OMEGA BLOCK(2)
    add.err <- 0.1
  })
  model({
    cl <- exp(tcl + eta.cl)
    v <- exp(tv + eta.v)
    ke <- cl / v
    d/dt(A1) = -ke * A1
    cp = A1 / v
    cp ~ add(add.er)
  })
}


```
